### 2023-03-12 paper.tex
added presentation
updated presentation

\begin{IEEEkeywords}
    robotics, programming, concepts, AI, augmented reality, virtual reality 
\end{IEEEkeywords}

@@

 \begin{itemize}
    \item Online Concepts
        \begin{itemize}
            \item Teach-in
            \item Master-Slave
            \item Vision-Based
        \end{itemize}
    \item Offline Concepts
        \begin{itemize}
            \item CAD/graphical based
            \item text based
            \item task based
        \end{itemize}
    \item Hybrid Concepts
 \end{itemize}

@@

        CAD based programming environments offer a mathematical approach to the programming workflow by adding different models and CAT based tools.
        Models could range from simple models of movements to more complex simulation models of the environment and the robot itself. %TODO cite this

>>>>

\begin{IEEEkeywords}
    robotics, programming, concepts, augmented reality, virtual reality 
\end{IEEEkeywords}

@@

 \begin{itemize}
    \item Online Concepts
        \begin{itemize}
            \item Teach-in
            \item Master-Slave
            \item Vision-Based
        \end{itemize}
    \item Offline Concepts
        \begin{itemize}
            \item CAD/graphical based
            \item text based
            \item task based
        \end{itemize}
 \end{itemize}

@@

        CAD based programming environments offer a mathematical approach to the programming workflow by adding different models and CAD based tools.
        Models could range from simple models of movements to more complex simulation models of the environment and the robot itself. %TODO cite this
